Follow-up Samples

### 2016-12-16 submission/manuscript_outline_20161024.Rmd
update manuscript refs 1st paragraph

Colorectal cancer (CRC) continues to be a leading cause of cancer related deaths and is the second most common cancer death among men aged 40-79 years of age (**insert citation**).  Over the last few years death due to the disease has seen a significant decrease thanks mainly to improvements in screening (**insert citation**).  However, despite this giant improvement there are still approximately 50,000 deaths from the disease a year (**insert citation**).  It is estimated that around 5-10% of all CRCs can be explained by autosomal dominant inheritance (**insert citation**). The vast majority of CRCs are not inherited and the exact etiology to disease has not been well worked out (**insert citation**).

>>>>

Colorectal cancer (CRC) continues to be a leading cause of cancer related deaths and is the second most common cancer death among men aged 40-79 years of age [@jemal_cancer_2010; @haggar_colorectal_2009].  Over the last few years death due to the disease has seen a significant decrease thanks mainly to improvements in screening [@jemal_cancer_2010].  However, despite this giant improvement there are still approximately 50,000 deaths from the disease a year [@haggar_colorectal_2009].  It is estimated that around 5-10% of all CRCs can be explained by autosomal dominant inheritance [@green_very_2007]. The vast majority of CRCs are not inherited and the exact etiology to disease has not been well worked out [@haggar_colorectal_2009].

### 2016-12-16 submission/manuscript_outline_20161024.tex
update manuscript refs 1st paragraph

Colorectal cancer (CRC) continues to be a leading cause of cancer
related deaths and is the second most common cancer death among men aged
40-79 years of age (\textbf{insert citation}). Over the last few years
death due to the disease has seen a significant decrease thanks mainly
to improvements in screening (\textbf{insert citation}). However,
despite this giant improvement there are still approximately 50,000
deaths from the disease a year (\textbf{insert citation}). It is
estimated that around 5-10\% of all CRCs can be explained by autosomal
dominant inheritance (\textbf{insert citation}). The vast majority of
CRCs are not inherited and the exact etiology to disease has not been
well worked out (\textbf{insert citation}).

@@

\subsection{References}\label{references}

>>>>

Colorectal cancer (CRC) continues to be a leading cause of cancer
related deaths and is the second most common cancer death among men aged
40-79 years of age (1, 2). Over the last few years death due to the
disease has seen a significant decrease thanks mainly to improvements in
screening (1). However, despite this giant improvement there are still
approximately 50,000 deaths from the disease a year (2). It is estimated
that around 5-10\% of all CRCs can be explained by autosomal dominant
inheritance (3). The vast majority of CRCs are not inherited and the
exact etiology to disease has not been well worked out (2).

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-jemal_cancer_2010}{}
1. \textbf{Jemal A}, \textbf{Siegel R}, \textbf{Xu J}, \textbf{Ward E}.
2010. Cancer statistics, 2010. CA: a cancer journal for clinicians
\textbf{60}:277--300.
doi:\href{https://doi.org/10.3322/caac.20073}{10.3322/caac.20073}.

\hypertarget{ref-haggar_colorectal_2009}{}
2. \textbf{Haggar FA}, \textbf{Boushey RP}. 2009. Colorectal cancer
epidemiology: Incidence, mortality, survival, and risk factors. Clinics
in Colon and Rectal Surgery \textbf{22}:191--197.
doi:\href{https://doi.org/10.1055/s-0029-1242458}{10.1055/s-0029-1242458}.

\hypertarget{ref-green_very_2007}{}
3. \textbf{Green RC}, \textbf{Green JS}, \textbf{Buehler SK},
\textbf{Robb JD}, \textbf{Daftary D}, \textbf{Gallinger S},
\textbf{McLaughlin JR}, \textbf{Parfrey PS}, \textbf{Younghusband HB}.
2007. Very high incidence of familial colorectal cancer in Newfoundland:
A comparison with Ontario and 13 other population-based studies.
Familial Cancer \textbf{6}:53--62.
doi:\href{https://doi.org/10.1007/s10689-006-9104-x}{10.1007/s10689-006-9104-x}.
